Holomorphic field theories and higher algebra

### 2023-08-17 highervertexops.tex
expansion

Consider now  
\[
|(z,\lambda)|^2 \define z_1 \lambda_1 + z_2 \lambda_2, 
\]
which describes the evaluation pairing. 
It is preserved by the $SL(2)$-action, and hence we see that the canonical quotient map 
\[
q \colon \C[z_i,\lambda_i] \to \sfR = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
\]
is $SL(2)$-equivariant.
Moreover, inside $V_{a,b}$, any multiple of $|(z,\lambda)|^2$ is annihilated by $q$,
so $R$ is spanned by the images of $H_{a,b}$.
Thus, there is a direct sum decomposition $\sfR = \bigoplus_{a,b} \sfR_{a,b}$ where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.

@@

This lemma is proved by applying the description of the decomposition into irreducibles.

@@

\begin{cor}
The differential $\dbar$ is an isomorphism from $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$ for $b > 0$.
Thus, the cohomology is 
\[
H^0(A) = \bigoplus_{a \in \NN} \sfR_{a,0}
\]
and
\[
H^1(A) = \bigoplus_{b \in \NN} \sfR_{0,b}.
\]
\end{cor}

@@

Note that $p$ is not a map of algebras. 
For example,
\beqn
p(z_1 \lambda_1) = \frac12
\eeqn
as $z_1 \lambda_1$ admits a $\lie{sl}(2)$-decomposition
\beqn
z_1 \lambda_1 = \frac12 (z_1 \lambda_1 - z_2 \lambda_2) + \frac12 .
\eeqn

\subsection{The higher algebraic residue}

Define
\beqn
\op{Res} \colon \sfA \to \C[-1]
\eeqn
by the rules that $\op{Res}|_{\sfA^0} = 0$ and
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
\eeqn
This residue extends to the completion to give a map
\beqn
\op{Res} \colon \laurent \to \C[-1] .
\eeqn

@@

Let $J$ be the map
\beqn
J \colon \sfA \to \cP_2
\eeqn
defined by sending an element $a \in \sfA$ to the quadratic functional
\beqn
J_a (\beta \gamma) = \Res(\beta a \gamma) .
\eeqn

\begin{lem}
The map $J$ is a cochain map.
Furthermore, for any $a,a' \in \sfA$ we have $\{J_a, J_{a'}\} = 0$.
Thus, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
\end{lem}
\begin{proof}
For the first claim observe that
\beqn
J_{\dbar a} (\beta \gamma) = \Res(\beta (\dbar a) \gamma) = \pm \Res((\dbar \beta) a \gamma) \pm \Res(\beta a \dbar \gamma) = J_a (\dbar \beta \gamma) + (-1)^{|\beta|} J_a(\beta \dbar \gamma) 
\eeqn
by (3) in lemma \ref{lem:res}.
\end{proof}

>>>>

Consider now  
\[
|(z,\lambda)|^2 \define z_1 \lambda_1 + z_2 \lambda_2, 
\]
which describes the evaluation pairing. 
It is preserved by the $SL(2)$-action, and hence we see that the canonical quotient map 
\[
q \colon \C[z_i,\lambda_i] \to \sfR = \C[z_i,\lambda_i]/(|(z,\lambda)|^2 = 1)
\]
is $SL(2)$-equivariant.
Moreover, inside $V_{a,b}$, any multiple of $|(z,\lambda)|^2$ is annihilated by $q$,
so $R$ is spanned by the images of $H_{a,b}$.
Thus, there is a direct sum decomposition 
\beqn
\sfR = \bigoplus_{a,b} \sfR_{a,b}
\eeqn
where $\sfR_{a,b} = q(H_{a,b})$ is the image of the subspace of harmonic polynomials in $\C[z_i,\lambda_i]$ under the quotient map.
We remark that this decomposition does \textit{not} respect the commutative product.

@@

This lemma is proved by applying the description of the decomposition into irreducibles.
In turn, any polynomial $f(z,\lambda) \in \sfR$ admits a decomposition of the form
\beqn\label{eqn:expand}
f(z, \lambda) = \sum_{a,b,k \geq 0} c_{k}^{ab} \sff^k (z_1^a \lambda_2^b) 
\eeqn
for some coefficients $c_k^{ab}$.

@@

\begin{cor}
The differential $\dbar$ is an isomorphism from $\sfR_{a,b}$ to $\sfR_{a+1,b-1} \omega$ for $b > 0$.
Thus, the cohomology of $\sfA$ is 
\[
H^0(\sfA) = \bigoplus_{a \in \NN} \sfR_{a,0}
\]
and
\[
H^1(\sfA) = \bigoplus_{b \in \NN} \sfR_{0,b}.
\]
\end{cor}

@@

Note that $p$ is not a map of algebras. 
For example,
\beqn
p(z_1 \lambda_1) = \frac12
\eeqn
as $z_1 \lambda_1$ admits a $\lie{sl}(2)$-decomposition
\beqn
z_1 \lambda_1 =  \frac12  + \frac12 (z_1 \lambda_1 - z_2 \lambda_2).
\eeqn
\subsection{The higher algebraic residue}

Define
\beqn
\op{Res} \colon \sfA \to \C[-1]
\eeqn
by the rules that $\op{Res}|_{\sfA^0} = 0$ and
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
\eeqn
In terms of the expansion \eqref{eqn:expand} we have
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = c_{0}^{00} .
\eeqn

This residue extends to the completion to give a map
\beqn
\op{Res} \colon \laurent \to \C[-1] .
\eeqn

@@

Let $J$ be the map
\beqn
J \colon \laurent \to \cP_2
\eeqn
defined by sending an element $a \in \sfA$ to the quadratic functional
\beqn
J_a (\beta \gamma) = \Res(\beta a \gamma) .
\eeqn

\begin{lem}
The following are true of the map $J$.
\begin{enumerate}
\item $J$ is a cochain map.
\item $J$ is $\lie{sl}(2)$-equivariant.
\item For $a,a' \in \laurent$ one has $\{J_a, J_{a'}\} = 0$.
\end{enumerate}
In particular, if we endow $\sfA$ with the structure of an abelian dg Lie algebra then $J$ is a map of dg Lie algebras.
\end{lem}
\begin{proof}
For the first claim observe that
\beqn
J_{\dbar a} (\beta \gamma) = \Res(\beta (\dbar a) \gamma) = \pm \Res((\dbar \beta) a \gamma) \pm \Res(\beta a \dbar \gamma) = J_a (\dbar \beta \gamma) + (-1)^{|\beta|} J_a(\beta \dbar \gamma) 
\eeqn
by (3) in lemma \ref{lem:res}.
\end{proof}
